---
title: "project"
author: "Ella van Engen and Connor Wilchusky"
date: "3-21-21"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
library(tidyverse)
```

```{r}
glimpse(set1)
glimpse(set2)
glimpse(set3)
```


Research Question for Dataset 1 (Colleges): Is there any correlation between mid-career salary and the percentage of of alumni who think they are making the world a better place across all North Carolina colleges? 
Hypothesis for Dataset 1: There will be no correlation between mid-career salary and the percentage of alumni who believe they are making the world a better place across North Carolina colleges.  

Research Question for Dataset 2 (Transit): Is the cost per km of urban rail more dependent on the time length of the project or the total rail length of the project?
Hypothesis for Dataset 2: Cost per km of urban rail is more dependent on the total rail length of the project. 

Research Question for Dataset 3 (Spotify):
Hypothesis for Dataset 3:
